\documentclass[11pt]{article}
\usepackage[letter, top=1.3cm, left=1.5cm, bottom=1.3cm, right=1.2cm]{geometry}
\usepackage{anyfontsize}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{setspace}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage[sfdefault,light]{roboto}

\pagenumbering{gobble}
\setlength{\parindent}{0}

\begin{document}

\bgroup{}
\def\arraystretch{1.3}%
\begin{tabularx}{\textwidth}{X r}
    \multirow{3}{*}{\fontsize{50}{60}\fontseries{t}\selectfont Vivek \fontseries{l}\selectfont ROY} & {\faEnvelope}~~vivek@vivekroy.com \\
    & {\large \faPhone}~~(+91) 9800-855-853 \\
    & {\faLink}~~https://vivekroy.com
\end{tabularx}
\egroup{}

\vspace{1cm}

\begin{tabularx}{\textwidth}{l X}
    {\fontseries{r}\selectfont \LARGE EDUCATION} & {\midrule} \\
\end{tabularx}

\bgroup{}
\def\arraystretch{1.1}%
\begin{tabularx}{\textwidth}{l X r}
    {\small 2015--19} & {\fontseries{r}\selectfont {\large Jadavpur University}} & {\small Kolkata, India} \\
                & {Bachelor's degree (B.E.) in Computer Science \& Engineering} & \\
                & {\hspace{2ex} \small CGPA: 8.6/10.0} & \\[1.5ex]
    {\small 2013--15} & {\fontseries{r}\selectfont {\large D.A.V Model School}} & {\small Durgapur, India} \\
                     & {Senior Secondary Education (Class 12)} & \\
                     & {\hspace{2ex} \small Marks: 93.6\%} & \\[1.5ex]
    {\small 2002--13} & {\fontseries{r}\selectfont {\large St. Xavier's School}} & {\small Durgapur, India} \\
                     & {Secondary Education (Class 10)} & \\
                     & {\hspace{2ex} \small Marks: 94\%} & \\[1.5ex]
\end{tabularx}
\egroup{}

\vspace{0.5cm}

\begin{tabularx}{\textwidth}{l X}
    {\fontseries{r}\selectfont \LARGE INTERNSHIPS} & {\midrule} \\
\end{tabularx}

\bgroup{}
\def\arraystretch{1.1}%
\begin{tabularx}{\textwidth}{l X r}
    {\small Jun '18 --} & {\fontseries{r}\selectfont {\large Carnegie Mellon University, RISS 2018}} & {\small Pittsburgh, PA, USA} \\
    {~~\small Aug '18} & {Guided by Dr. Martial Hebert} & \\
                & {Visual Object Tracking using Optical Flow as input to a CNN.} & \\[1.5ex]
    {\small Jun '17 --} & {\fontseries{r}\selectfont {\large Student Developer, Google Summer of Code 2017}} & {\small GSoC 2017} \\
    {~~\small Aug '17} & {GSoC 2017 under Haiku Inc.} & \\
                     & {3D Hardware accelerated graphics drivers for Haiku OS.} & \\[1.5ex]
\end{tabularx}
\egroup{}

\vspace{0.5cm}

\begin{tabularx}{\textwidth}{l X}
    {\fontseries{r}\selectfont \LARGE RESEARCH} & {\midrule} \\
\end{tabularx}

\bgroup{}
\def\arraystretch{1.1}%
\begin{tabularx}{\textwidth}{l X r}
    {\small Sep '18 --} & {\fontseries{r}\selectfont {\large Image Captioning}} & {\small Jadavpur Univ.,} \\
    {~~\small Present} & {Guided by Dr. Sanjoy Kumar Saha} & {\small Kolkata, India}\\
                     & {Automatic generation of image captions. Work in progress. Experimenting with Generative Adversarial Networks and Capsule Networks.} & \\[3.5ex]
    {\small Nov '17 --} & {\fontseries{r}\selectfont {\large Visual Odometry using Deep learning}} & {\small Jadavpur Univ.,} \\
    {~~\small Aug '18} & {Guided by Dr. Sanjoy Kumar Saha} & {\small Kolkata, India}\\
                     & {Feature point selection using Deep learning combined with geometrical tracking for real-time performance. To be deployed on an autonomous robot developed by Jadavpur University.} & \\[5.5ex]
    {\small Apr '17 --} & {\fontseries{r}\selectfont {\large Policy non-compliance detection from log records}} & {\small DRDO} \\
    {~~\small Jan '18} & {Guided by Prof. Chandan Mazumdar} & {\small New Delhi, India} \\
                       & {Funded by Defence Research and Development Organisation (DRDO), Govt.\ of India.} & \\
                       & {Natural Language Processing of log records and policies to detect non-compliance and report security vulnerabilities. Deployed in DRDO log servers for offline log record analysis.} & \\[5.5ex]
\end{tabularx}
\egroup{}

\vspace{0.5cm}

\begin{tabularx}{\textwidth}{l X}
    {\fontseries{r}\selectfont \LARGE ACHIEVEMENTS \& AWARDS} & {\midrule} \\
\end{tabularx}

\bgroup{}
\def\arraystretch{1.1}%
\begin{tabularx}{\textwidth}{l X}
    {\small 2013} & {{\fontseries{r}\selectfont {\large National Talent Search Examination Scholarship}} winner for exceptional knowledge in the fields of Science and Social Science, awarded by NCERT, CBSE, Govt. of India.} \\[3.5ex]
    {\small 2012--14} & {Cleared {\fontseries{r}\selectfont {\large Regional Mathematics Olympiad}} and shortlisted for {\fontseries{r}\selectfont {\large Indian National Mathematics Olympiad}} 3 years in a row. (Top 200 among 20,000 students).} \\[3.5ex]
    {\small 2014} & {Cleared {\fontseries{r}\selectfont {\large Zonal Informatics Olympiad}} and shortlisted for {\fontseries{r}\selectfont {\large Indian Computing Olympiad}} (Top 100 among 10,000 students).} \\[3.5ex]
\end{tabularx}
\egroup{}

\vspace{0.8cm}

\begin{tabularx}{\textwidth}{l X}
    {\fontseries{r}\selectfont \LARGE POSITIONS of RESPONSIBILITY} & {\midrule} \\
\end{tabularx}

\bgroup{}
\def\arraystretch{1.1}%
\begin{tabularx}{\textwidth}{l X}
    {\small 2016--Present} & {{\fontseries{r}\selectfont {\large Student Convener, CodeClub, Jadavpur University}}, a club dedicated to teaching competitive programming.} \\[3.5ex]
    {\small 2016--Present} & {{\fontseries{r}\selectfont {\large Volunteer, Science club, Jadavpur University}}. Teaching basic math and science to underprivileged children.} \\[3.5ex]
    {\small 2016--Present} & {{\fontseries{r}\selectfont {\large Mentor, JontroTontro (annual robotics event), Jadavpur University}}. Organising workshops on robotics, computer vision and image processing. Mentoring freshmen year teams for robotics competition.} \\[5.5ex]
\end{tabularx}
\egroup{}

\vspace{0.8cm}

\begin{tabularx}{\textwidth}{l X}
    {\fontseries{r}\selectfont \LARGE SKILLS} & {\midrule} \\
\end{tabularx}

\hspace{0.4cm}\bgroup{}
\def\arraystretch{1.5}%
\begin{tabularx}{\textwidth}{X X X X}
    {{\fontseries{r}\selectfont {\large Languages}} \begin{itemize}[leftmargin=1em]
            \setlength\itemsep{0}
            \setlength{\parskip}{2pt}
            \item Python
            \item C++
            \item C
            \item Rust
            \item Java
            \item Javascript
            \item Shell
            \item MATLAB
        \end{itemize}} &
    {{\fontseries{r}\selectfont {\large Tools \& Libraries}} \begin{itemize}[leftmargin=1em]
            \setlength\itemsep{0}
            \setlength{\parskip}{2pt}
            \item OpenCV
            \item Qt
            \item Latex
            \item CMake
            \item Android
        \end{itemize}} &
    {{\fontseries{r}\selectfont {\large DL Frameworks}} \begin{itemize}[leftmargin=1em]
            \setlength\itemsep{0}
            \setlength{\parskip}{2pt}
            \item Tensorflow
            \item PyTorch
            \item Keras
        \end{itemize} \vspace{0.4cm} {\fontseries{r}\selectfont {\large Databases}}
        \begin{itemize}[leftmargin=1em]
            \setlength\itemsep{0}
            \setlength{\parskip}{2pt}
            \item MySQL
            \item MongoDB
        \end{itemize}
    } &
    {{\fontseries{r}\selectfont {\large Web Backend}} \begin{itemize}[leftmargin=1em]
            \setlength\itemsep{0}
            \setlength{\parskip}{2pt}
            \item Go
            \item NodeJS
            \item Django (Python)
        \end{itemize} \vspace{0.4cm} {\fontseries{r}\selectfont {\large Web Frontend}}
        \begin{itemize}[leftmargin=1em]
            \setlength\itemsep{0}
            \setlength{\parskip}{2pt}
            \item ReactJS
            \item VueJS
        \end{itemize}
    } & \\
\end{tabularx}
\egroup{}

\end{document}
